Demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism

### 2025-08-28 Manuscript/ant_cactus_SUBMISSION2.tex
fixing appendix lettering

@@

@@

@@

%% Seeds Produced
\paragraph{Seeds Per Flower Model}

@@

Each viable flower on a plant produces between 97 and 257 seeds (Figure \ref{app:seeds}).
This number is affected by the ant partner present, as shown in previous work \citep{Ohm2014}. 
\textit{C. opuntiae} tended plants produce a mean of 115 seeds per flower. 
\textit{L. apiculatum} tended plants produce a mean of 143 seeds per flower.
Vacant plants produce a mean of 148 seeds per flower. 
Comparison between posterior distributions revealed that \textit{C. opuntiae} tended plants produced fewer seeds per flower than \textit{L. apiculatum} tended plants and vacant plants 80\% and 87\% of the time.
Vacant plants produced more seeds per flower than \textit{L. apiculatum} tended plants only 57\% of the time.

@@

	%% Germination
	\paragraph{Germination Model}
	Seeds have a slightly higher probability of germinating in year one than in year two.
	Seeds in year one experience germination rates between 50\% and 100\% with a mean of 62\% germination.
	Seeds in year two experience germination rates between 50\% and 98\% with a mean of 58\% germination.

@@

>>>>

\renewcommand{\thefigure}{B\arabic{figure}}

@@

\renewcommand{\thefigure}{C\arabic{figure}}

@@

\renewcommand{\thefigure}{D\arabic{figure}}

@@

%% Seeds Produced
\paragraph{Seeds Per Fruit Model}

@@

Each viable flower on a plant produces between 97 and 257 seeds (Figure \ref{app:seeds}).
This number is affected by the ant partner present, as shown in previous work \citep{Ohm2014}. 
\textit{C. opuntiae} tended plants produce a mean of 115 seeds per flower. 
\textit{L. apiculatum} tended plants produce a mean of 143 seeds per flower.
Vacant plants produce a mean of 148 seeds per flower. 
Comparison between posterior distributions revealed that \textit{C. opuntiae} tended plants produced fewer seeds per flower than \textit{L. apiculatum} tended plants and vacant plants with 80\% and 87\% confidence, respectively.
%Vacant plants produced more seeds per flower than \textit{L. apiculatum} tended plants only 57\% of the time.

@@

	%% Germination
	\paragraph{Germination Model}
	Seeds have a slightly higher probability of germinating in year one than in year two.
	\tom{Seeds in year one experience germination rates between 50\% and 100\% with a mean of 62\% germination.
	Seeds in year two experience germination rates between 50\% and 98\% with a mean of 58\% germination.}{I do not understand what these ranges are.}

@@

\renewcommand{\thefigure}{E\arabic{figure}}
